RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-23 manuscripts/manuscript.Rmd
added citation to Stolzfus et al (#58)

Though R provides the most extensive and widely used collection of
comparative phylogenetic methods tools, R users lack a convenient,
extensible format to exchange and archive comparative methods data.
A common file format for sharing phylogenetic tree data has long played
an essential role in the advancement of phylogenetics research.
The rapid increase in phylogenetics data and research methods that make
use of such data has introduced many new challenges and opportunities 
to sharing this information both between software environments and 
between research groups `r citet("Drew PLOS Biology Tree of Life 2013")`.

>>>>

Though R provides the most extensive and widely used collection of
comparative phylogenetic methods tools, R users lack a convenient,
extensible format to exchange and archive comparative methods data.
A common file format for sharing phylogenetic tree data has long played
an essential role in the advancement of phylogenetics research.
The rapid increase in phylogenetics data and research methods that make
use of such data has introduced many new challenges and opportunities 
to sharing this information both between software environments and 
between research groups `r citep(c("Drew PLOS Biology Tree of Life 2013", "10.1186/1756-0500-5-574"))`.
